Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-12 paper/tex/introduction.tex
clarifying sensitivity analysis

This paper is distinguished from other comparisons of \pz\ methods by its focus on the evaluation criteria for \pzpdf s and interpretation thereof.
In the absence of simulated data drawn from known redshift distributions, the very concept of a ``true PDF'' for an individual galaxy is unavailable, and we must instead rely on measures of ensemble behaviour to characterize PDF quality (see \S\,\ref{sec:metrics} for further discussion).
We aim to perform a comprehensive sensitivity analysis of \pzpdf\ techniques in order to ultimately select those that will become part of the \lsstdesc\ pipelines, described in the Science Roadmap (SRM)\footnote{Available at: \url{https://lsstdesc.org/assets/pdf/docs/DESC_SRM_latest.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a formally controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.

>>>>

This paper is distinguished from other comparisons of \pz\ methods by its focus on the evaluation criteria for \pzpdf s and interpretation thereof.
In the absence of simulated data drawn from known redshift distributions, the very concept of a ``true PDF'' for an individual galaxy is unavailable, and we must instead rely on measures of ensemble behaviour to characterize PDF quality (see \S\,\ref{sec:metrics} for further discussion).
We aim to perform a comprehensive sensitivity analysis of the dependence of \pzpdf s on the code used to produce them in order to ultimately select those that will become part of the \lsstdesc\ pipelines, described in the Science Roadmap (SRM)\footnote{Available at: \url{https://lsstdesc.org/assets/pdf/docs/DESC_SRM_latest.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a formally controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.
